Relationships in the extremes and their influence on competition and coexistence

### 2021-07-14 paper/Paper.Rnw
more work on intro and sentence strucutre

Asymmetries in tail associations have the potential to influence competition and coexistence via one particular mechanism, namely, storage effects. Covariation between environmental fluctuations and competitive pressures allows for storage effect to be a contributing stabalizing mechanism to coexistence. Because the contributive value of storage effects relies on the association of competition and environment (Chesson 1994, Barbaras ..), it is reasonable to suspect the contribution of storage effects to coexistence can be altered by an association between competition and environment that is asymmetric. While we aimed to investigate the importance of ATAs on coexistence in general and all the mechanisms which compose the modern theory of coesustence, it was quickly revealed that ATAs are specifically important for storage effects and not for other mechanisms on coexistence (due to the fact that storage effect is the only mechanism that depends of the variance between two drivers).

@@

[As we know], anthropogenic climate change has large consequences for almost all aspects of life including via extreme climatic events, which have only become more extreme - increasing in magnitude and frequency - and have contributed to the increase in global means as well as an increase in environmental variability. While there are multiple studies on the influence of environmental extremes and varaibility on competition and coexistence (Parepa et al 2013, Diez et al 2012), the influence of relationships and interactions between drivers in their extremes, has not yet been explored. By definition, interacting environmental drivers that are  moreso related in the extreme values are tail associated, thus we have implemented our tools for the study of tail associations to explore the importance of environmental relationships in their exrtemes on competition and coexistence. Environmental variability has been classically shown to promote coexistence via storage mechanisms (Chesson and Warner 1981, Warner and Chesson 1985), hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental variables on the contribution of storage effects to coexistence.

>>>>

Asymmetries in tail associations can potentially influence competition and coexistence via one particular mechanism, namely, storage effects.
Storage effect contributes as a stabilizing mechanism to coexistence when there is covariation between competitive pressures and environmental fluctuations.
Because the contributive value of storage effects relies on the relationship between environment and competition (Chesson 1994, Barbaras ..), it reasonably follows to suspect the contribution of storage effectsto be altered by an association between environment and competition that is asymmetric, i.e., ATAs between environment and competition.
Uniquely, storage effect is the only mechanism of modern coexistence theory which depends on the variance between two drivers rather than one.
While we aimed to investigate the importance of ATAs on coexistence in general and all the mechanisms which compose the modern theory of coexistence, it was quickly revealed that ATAs are specifically important for storage effects and not for other mechanisms of coexistence.

@@

[As we know], anthropogenic climate change has large consequences for almost all aspects of life including via extreme climatic events, which have only become more extreme - increasing in magnitude and frequency - and have contributed to both the increase in global means as well as an increase in environmental variability. 
There are many studies on the influence of environmental extremes and variability on competition and coexistence (Parepa et al 2013, Diez et al 2012); however, the study of the influence of relationships and interactions between drivers in their extremes on competition and coexistence, is lacking in the scientific literature. 
Interacting environmental drivers can be asymmetrically related in the extreme values (as shown in Gosh et al 2020 AER). Thus we have implemented our tools for the study ATAs to explore the importance of environmental relationships in their extremes on competition and coexistence. 
Environmental variability has been classically shown to promote coexistence via storage mechanisms in a lottery model of competition (Chesson and Warner 1981, Warner and Chesson 1985), hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental variables on the contribution of storage effects to coexistence.
